---
title: "MFX function"
author: "Yilun"
date: "6/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mfx)
```
## Creating Data
x is a continous data
```{r}
set.seed(12345)
n = 1000
x = rnorm(n) 
y = ifelse(pnorm(1 + 0.5 * x + rnorm(n)) > 0.5, 1, 0)
my.data = data.frame(y, x)
```
## running a probit model
```{r}

my.mod1 = probitmfx(formula = y ~ x, data = my.data)
my.mod1$mfxest
```

## Tasks
 * It is ok to assume there is only one variable called x 
 * The functions accepts a formula and a dataset 
 * There is a boolean variable atmean, with default TRUE. If TRUE the function calculates the partial effect at the average (inserting ¯x) 
 * If atmean=FALSE the function calculates the average of the partial effects
```{r}
my.mfx = function(formula, data, atmean = TRUE){
  #estimate Model
  my.glm=glm(formula = formula,family = binomial(link = "probit"),data = data)
  beta = unname(my.glm$coefficients[1])
  beta.x =unname(my.glm$coefficients[2])
  if(atmean){
    #calculate PEA
    x.mean = mean(my.glm$model$x) 
    result = c(dnorm(beta+x.mean*beta.x)*beta.x)
  } else {
    #calculate APE
    result = c(
      mean(
        dnorm(beta+my.glm$model$x*beta.x)*beta.x
      )
    )
  }
  #add name
  names(result)= c("Marginal Effect")
  return(result)
}

# Test
## PEA
my.mfx(formula = y ~ x, data=my.data)
probitmfx(formula = y ~ x, data = my.data)
## APE
my.mfx(formula = y ~ x, data=my.data, atmean = FALSE)
probitmfx(formula = y ~ x, data = my.data, atmean=FALSE)
```
 
 