---
title: "LPM Model fit problem"
author: "Yilun"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
   html_document:
    #variant: markdown_github
    toc: true
    number_sections: false
    self_contained: no
    toc_depth: 4
    toc_float: true
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(wooldridge)
library(dplyr)
data("k401ksubs")
```

There has been much interest in the question whether the presence of 401(k) pension plans, available to many U.S. workers, increases net savings.  

The data set k401KSUBS contains information on net ﬁnancial assets (`nettfa`), family income (`inc`), a binary variable for eligibility in a 401(´k´) plan (´e401k´), and several other variables. In the following, you are asked to run a linear regression that predicts eligibility.

```{r}
glimpse(k401ksubs)
```

## 1 Tasks 
### 1.1 Fitting and interpreting
* How many families are eligible and how many are not eligible for participation in a 401(k) plan? Present the absolute numbers and the respective fractions.
```{r}
absElig = sum(k401ksubs$e401k)
relElig = round(absElig/nrow(k401ksubs)*100,2)
```
  
  + `r absElig` Families are eligible for participation, `r relElig`% of all families

* Estimate a linear probability model explaining 401(k) eligibility in terms of income, age, and gender. Include income and age in quadratic form, and report the results in the usual form.

```{r}
lm_elig = lm(e401k ~ inc + incsq + age + agesq + male, k401ksubs)
summary(lm_elig)
```
* Interpret the coeﬃcients.
* Obtain the ﬁtted values from the linear probability model estimated in part (ii). Are any ﬁtted values negative or greater than one?
```{r echo = TRUE}
elig.fitted = fitted.values(lm_elig)
# Counter: Fitted Values > 1 
sum(elig.fitted >1)
# Counter: Fitted Values negative
sum(elig.fitted <0)
```

### 1.2 Discussing model fit
* Using the ﬁtted values $\widehat{e401k}_{i}$ from part (iv), deﬁne $\widetilde{e401k}_{i}=1$ if $\widehat{e401k}_{i} \ge 0.5$ and $\widetilde{e401k}_{i}=0$  if $\widehat{e401k}_{i} < 0.5$ . Out of 9,275 families, how many are predicted to be eligible for a 401(k) plan?
```{r}
classify.elig.int = function(value,threshold){
  if(value >= threshold){
    return(1) 
  }
   else {
    return(0)
  }
}

elig.predicted = sapply(elig.fitted,classify.elig.int,threshold = 0.5)
sum(elig.predicted)
```

* Use the variable $\widetilde{e401k}_{i}$ to compute the overall percent of correctly predicted/classiﬁed observations (families).
```{r}
# Create new Variable storing results
newData= data.frame(elig=k401ksubs$e401k) #Train Data
newData$elig.predict=elig.predicted #Test Data
newData$eval = newData$elig - newData$elig.predict #Result Evaluation

nrow(filter(newData,eval == 0))/nrow(newData)

```

* Now compute the percent correctly predicted/classiﬁed for both eligible and non-eligible families. What does this suggest regarding your previously computed measure of model ﬁt?
```{r}
#eligible prediction accuracy
nrow(filter(newData,elig == 1, eval == 0))/nrow(newData)
#non-eligible prediction accuracy
nrow(filter(newData,elig == 0, eval == 0))/nrow(newData)
```
the overall percent of correct predictions is the sum of correct eligible and non-eligible predictions

### 1.3 Writing a function
Now write a function that accepts a vector thresholds for predicting a family as eligible vs non-eligible. For example, the function accepts `c(0.5, 0.6)` as an input parameter.

The function takes the data and the formula as an input. The function performs the following steps:

* It runs the regression (speciﬁed in the formula-argument)
* Then, it uses the threshold and computes the overall percent of correctly classiﬁed observations and also the the percent correctly predicted/classiﬁed for both eligible and non-eligible families.

```{r echo = TRUE}
# function for classifing, using a vector
classify.elig.vec = function(value,threshold){
  Tmin=min(threshold)
  Tmax=max(threshold)
  if(Tmax>=value&value>=Tmin ){
    return(1) 
  }
   else {
    return(0)
  }
}

analyse.accuracy = function(data,formula,threshold){
  #run regression
  lm_data = lm(formula = formula,data=data)
  
  #extract values 
  fitted_data=fitted.values(lm_elig)
  model_data=data.frame(Original=data$e401k)
  ##predict classification and add to data frame
  model_data$Prediction = sapply(fitted_data,classify.elig.vec,threshold = threshold)
  ##evaluate prediction
  model_data$eval = model_data$Original - model_data$Prediction
  
  # analyse 
  Accuracy = list(
    Overall = nrow(filter(model_data,eval == 0))/nrow(model_data),
    Eligible = nrow(filter(model_data,Original == 1, eval == 0))/nrow(model_data),
    NonEligible = nrow(filter(model_data,Original == 0, eval == 0))/nrow(model_data)
  )
  #output result
  return(Accuracy)
}

#testing
analyse.accuracy(k401ksubs,"e401k ~ inc + incsq + age + agesq + male",c(0.5,0.6))

```


