---
title: "*apply Functions"
author: "Yilun"
date: "4/27/2021"
output:
   html_document:
    #variant: markdown_github
    toc: true
    number_sections: false
    self_contained: no
    toc_depth: 2
    toc_float: true
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

`lapply` returns a list of the same length as X, each element of which is the result of applying `FUN` to the corresponding element of `X`. Results are stored as list

`sapply` is same as `lapply` but tries to simplify the result. Results are stored as vector(if possible, otherwise returns list)

`mapply` Multivariate version of `sapply`

`apply` is used to apply a function (often anonymous one) over the margins of an array (vector). 

## Remark: *apply vs. for loops

 * apply functions are fast (usually) 
 * there are special packages so that apply functions can be calculated parallel on multicore systems → super-fast 
 * **but**: each element is calculated separately; calculations that depend on the outcome of previous elements are not possible with *apply but with for loops.
 
## Excersice
Idea: 10 samples, each of length 30 Each column in the matrix should be one sample

```{r}
my.rnorm.vector = rnorm(n = 10*30, mean = 0, sd = 1) 
my.matrix = matrix(my.rnorm.vector, nrow=30, ncol=10)

# Inspecting
head(my.matrix)
```

### Task


1. Implement a function that takes the matrix as an input. The function computes the mean and the sample variance for each sample and returns a list of two elements.

```{r}
my.fun.calc.summary = function(input){
  vec.means = apply(input,MARGIN = 2, FUN = mean)
  vec.var = apply(input,MARGIN = 2, FUN = var)
  result = list(means = vec.means, variances = vec.var)
  return(result)
}

# Checking:
my.result = my.fun.calc.summary(my.matrix)
my.result
str(my.result)
```

2. Implement a modiﬁed function that returns a matrix where the ﬁrst column is the column of means and the second is the column of variances.

```{r}
my.fun.calc.summary.v2 = function(input){
  means = apply(input,MARGIN = 2, FUN = mean)
  variances = apply(input,MARGIN = 2, FUN = var)
  result = matrix(c(means, variances), ncol = 2, byrow = FALSE)
  colnames(result) = c("means","variances")
  return(result)
}

# Checking:
my.fun.calc.summary.v2(my.matrix)
```

3. Up to now the simulated data is static. Write a function my.simulation that has two arguments for the sample size `size` and the number of samples `nr.sample`. This ﬁrst  generates the data and then calls your summary function to compute the summaries.

```{r}
my.simulation = function(nr.sample,size){
  my.rnorm.vector = rnorm(n = size*nr.sample, mean = 0, sd = 1) 
  my.matrix = matrix(my.rnorm.vector, nrow=size, ncol=nr.sample)
  my.fun.calc.summary.v2(my.matrix)
}

#Checking
my.simulation(nr.sample = 4, size=30)
```

