---
title: "Data Frame"
author: "Yilun"
date: "4/20/2021"
output:
   html_document:
    #variant: markdown_github
    toc: true
    number_sections: false
    self_contained: no
    toc_depth: 2
    toc_float: true
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data frames are Data Sets with different data types. 

### Methods

Create a Data Frame: 

```{r}
# Definition of vectors
name <- c("Mercury", "Venus", "Earth", 
          "Mars", "Jupiter", "Saturn", 
          "Uranus", "Neptune")
type <- c("Terrestrial planet", 
          "Terrestrial planet", 
          "Terrestrial planet", 
          "Terrestrial planet", "Gas giant", 
          "Gas giant", "Gas giant", "Gas giant")
diameter <- c(0.382, 0.949, 1, 0.532, 
              11.209, 9.449, 4.007, 3.883)
rotation <- c(58.64, -243.02, 1, 1.03, 
              0.41, 0.43, -0.72, 0.67)
rings <- c(FALSE, FALSE, FALSE, FALSE, TRUE, TRUE, TRUE, TRUE)

# Create a data frame from the vectors
planets_df <- data.frame(name,type,diameter,rotation,rings)

str(planets_df)
```
***
Sorting Data

`order()` is a function that gives you the ranked position of each element when it is applied on a variable. This can be used to sort the data frame by a given column 

```{r}
planets_df[order(planets_df$diameter),]
```

`head()` or `tail()`: Quick Look into the dataset

`str()`: Overview of Data frame structure

  * The total number of observations
  
  * The total number of variables
  
  * A full list of the variables names 
  
  * The data type of each variable 
  
  * The first observations
  