---
title: "Regressionen"
author: "Yilun"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
   html_document:
    #variant: markdown_github
    toc: true
    number_sections: false
    self_contained: no
    toc_depth: 4
    toc_float: true
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(wooldridge)
library(ggplot2)
```

## Regression

### 1 Loading and inspectindg Data

```{r}
data(hprice1)
glimpse(hprice1)
```

### 2 A first regression 

```{r}
my.lm1 = lm(price~ sqrft, data = hprice1)
summary(my.lm1)
```


#### 2.1 Using predict for predictions 

```{r}
my.price.hat = predict(my.lm1)
head(my.price.hat)

```

### 3 Random data Subsets

A simple way of obtaining a random sample is the following:

• First, reorder rows randomly

• Second, take (for example) the ﬁrst 80 percent of the rows

```{r}
my.random.index <- sample(nrow(hprice1), replace = FALSE)
head(my.random.index)
```

### 4 Tasks

#### 4.1 my.RSS
Write a function my.RSS with two inputs: a string describing the formula and the dataset. The function carries out the regression and returns the RSS (residual sum of squares)

```{r}
my.RSS = function(my.str, my.data){
  sum(lm(my.str,data = my.data)$residuals^2)
}

#Testing
my.RSS(my.str = "price~sqrft", my.data = hprice1)
```

#### 4.2 my.data.select
Write a function that has two input arguments: a data and a number for the split (e.g. 0.8 for 80 percent). The function returns randomly selected training and test datasets

```{r}
my.data.select = function(my.data, split){
  nrow.train = round(nrow(my.data)*split,0)
  nrow.test = nrow(my.data)-nrow.train
  return(
    list(
      traindata = my.data[sample(nrow(my.data),nrow.train, replace = FALSE),],
      testdata = sample_n(my.data,nrow.test)
    )
  )
}
```

```{r}
# Testing 1
my.datasets = my.data.select(my.data = hprice1, split=0.8)
glimpse(my.datasets)

```

```{r}
# Testing 2
my.datasets <- my.data.select(my.data = hprice1, split=0.8)
glimpse(my.datasets)

my.formula <- as.formula("price ~ sqrft") 
my.lm2 <- lm(my.formula, data=my.datasets$traindata)
summary(my.lm2)

predict.test <- predict(my.lm2, newdata = my.datasets$testdata)
head(predict.test)

```

#### 4.3 my.RSSTrainTest
Write a function that accepts a formula, a dataset and split as an input. It creates the training and test datasets, and runs the regression using the training dataset. Finally, it calculates the RSS for the training dataset and the test dataset.


```{r}
my.RSS.calculator = function(input.lm, x, y) {
  sum(((input.lm$coefficients[1]+input.lm$coefficients[2]*x)-y)^2)
}
#Testing
my.RSS.calculator(input.lm = lm("price~sqrft", data = hprice1),x = hprice1$sqrft,y=hprice1$price)

```
```{r}
my.RSSTrainTest = function(formula,my.data,split){
  # create Datasets
  fn.dataset = my.data.select(my.data = my.data, split = split)
  ## subsetting 
  train.dataset = fn.dataset$traindata
  test.dataset = fn.dataset$testdata
  
  # get Model using traindata
  fn.lm = lm(formula, data = fn.dataset$traindata)
  
  # Use Make to make predictions
  train.dataset$prediction = predict(fn.lm)
  test.dataset$prediction = predict(fn.lm,newdata = test.dataset)
  
  # compute RSS
  list(
    rssTrain = my.RSS.calculator(input.lm = fn.lm,x = train.dataset$sqrft, y = train.dataset$price),
    rssTest = my.RSS.calculator(input.lm = fn.lm,x = test.dataset$sqrft, y = test.dataset$price)
  )

}

#Testing 
my.RSSTrainTest("price ~ sqrft", my.data=hprice1, split=0.8)

```

