---
title: "Control Flows"
author: "Yilun"
date: "4/20/2021"
output:
   html_document:
    #variant: markdown_github
    toc: true
    number_sections: false
    self_contained: no
    toc_depth: 2
    toc_float: true
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Functions
```{r eval=FALSE}
if(cond) expr

if(cond) cons.expr  else  alt.expr

ifelse(test,yes,no)

for(var in seq) expr

while(cond) expr

repeat expr

break

next
```

### Syntax

`cond`: A condition that results in a boolean

`var`: A variable 

`seq`: vector or list for comparing to `var`

`expr`,`cons.expr`: An expression in a formal sense. This is either a simple expression or a so called compound expression, usually of the form `{ expr1 ; expr2 }`.

***

## Exercises

### `if/else` vs `ifelse` vs logical subsetting

1. The following dataframe contains for 9 students the grades and the information whether the respective student cheated or not.
```{r}
df = data.frame(id = 1:9,

                grade = c(2, 5, 3, 1, 6, 1, 4, 3, 1),

                cheated = c(FALSE, TRUE, TRUE, FALSE, FALSE, FALSE, FALSE, FALSE, TRUE))
```

Those who cheated get a grade 5. Set the value of grade to 5 for all students who cheated. . .

a) using a `for` loop and `if` (loop over the row numbers)

```{r}
df = data.frame(id = 1:9,

                grade = c(2, 5, 3, 1, 6, 1, 4, 3, 1),

                cheated = c(FALSE, TRUE, TRUE, FALSE, FALSE, FALSE, FALSE, FALSE, TRUE))

for( i in seq_along(df$id)) {
  if(df$cheated[i]) 
    df$grade[i]=5
  print(df$grade[i])
}
```

b) using the vectorized version `ifelse`
```{r}
df = data.frame(id = 1:9,

                grade = c(2, 5, 3, 1, 6, 1, 4, 3, 1),

                cheated = c(FALSE, TRUE, TRUE, FALSE, FALSE, FALSE, FALSE, FALSE, TRUE))
df$grade = ifelse(df$cheated,5,df$grade)


```

c) using subsetting 
```{r}
df = data.frame(id = 1:9,

                grade = c(2, 5, 3, 1, 6, 1, 4, 3, 1),

                cheated = c(FALSE, TRUE, TRUE, FALSE, FALSE, FALSE, FALSE, FALSE, TRUE))

df$grade[df$cheated] = 5

```

Hints:

* Use `seq_along` to loop over the row number

* Subsetting means an expression similar to `x[x < 3]`

* You can select a variable of a dataframe by using `$`, e.g., `df$grade`

* Check your result by displaying df

### Loops: `for` vs `while`

2. In general, every for loop can be written as a `while` loop and vice versa. But in many cases, one of them is the better choice. Unfortunately, the author of the following loops did not make a good choice.

a) Rewrite the following `for` loop as a `while` loop

```{r eval= FALSE}
x <- NULL 
for (i in 1:99999999) { 
  x <- c(x, sample(x = 1:10, size = 1)) 
  if (sum(x) >= 100) break 
}
x
```
Why is this `for` loop dangerous?

Der Code kann nen weilchen brauchen bis es durch geht

```{r}
x = NULL
while(sum(x)<100) 
  x = c(x,sample(x= 1:10, size = 1))
x
```

b) Rewrite the following `while` loop as a `for` loop:
```{r eval= FALSE}
animals <- c("dog", "cat", "mouse", "snail") 
i <- 1 
while (i <= length(animals)) {
  print(animals[i])
i <- i + 1 }
```

```{r}
animals <- c("dog", "cat", "mouse", "snail") 
for(i in animals) 
  print(i)
```
***

Write a function `my.bivariate.dice` which rolls two dice `Nsample` times and computes the sum of the two dice. The arguments are:

* `die1` the elements of the first die with default 1,...,6

* `die2` the elements of the first die with default 1,...,6

* `prob1` the vector of probabilities for the first die, with default NULL

* `prob2` the vector of probabilities for the first die, with default NULL

* `Nsample` sample size with default 20

    ```{r}
    my.bivariate.dice <- function(die1=1:6, die2=1:6, prob1=NULL, prob2=NULL, Nsample=20){
      # missing(x)  - This will test whether an argument (x) within a function as been specified within the call.
      sample.die1 <- sample(die1, Nsample, replace = TRUE, prob = prob1)
      sample.die2 = sample(die2,Nsample,replace=TRUE,prob2)
      sample.sum = sample.die1+sample.die2
      return(sample.sum)
    }
    my.bivariate.dice()
```

Write a function `my.bivariate.dice.matrix` which simulates the previous experiment `Nreps` times. The function has one additional input argument `Nreps` governing the number of repetitions. The output of the function is a matrix where each columns is one sample (of size `Nsample`)

```{r}
  my.bivariate.dice.matrix = function( Nreps = 2,die1=1:6,die2=1:6,prob1=NULL,prob2=NULL,Nsample=20) {
    dice.matrix=matrix(NA,nrow = Nsample, ncol = Nreps)
    for (i in 1:Nreps) {
        dice.matrix[,i] = my.bivariate.dice(die1 = die1, die2 = die2, prob1 = prob1, prob2 = prob2, Nsample = Nsample)
    }
    return(dice.matrix)
  }

my.bivariate.dice.matrix(Nsample = 6)

```

