---
title: "Homework III, due May 27th"
author: 
- M Loecher
- Yilun Liu
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(titanic)
```

#### This homework is the absolute minimum extra work that you need to invest to keep up with the material in this course.

#### 1. Review your understanding of **linear regression** using the book [An Introduction to Statistical Learning](http://faculty.marshall.usc.edu/gareth-james/ISL/)
  * Read chapters 3.1, 3.2.1, 3.3.1 
  * Reproduce Lab Exercises 3.6.4 (Interaction Terms) and 3.6.6 (Qualitative Predictors)


#### 2. Excercise 
Load the `titanic` library and the `titanic_train` data. In the following we use `Survived` as the outcome (y):

##### Fit a model containing the interactions between `Sex` and `Pclass`. Interpret the coefficients.
```{r echo = FALSE}
lm.1=lm("Survived~Pclass*Sex",data = titanic_train)
summary(lm("Survived~Pclass*Sex",data = titanic_train))
```

###### Interpretation: 
   - The P values for all Coefficients are very small, which indicates a relationship between the choosen predictor (interaction between `Pclass` and `Sex`)  and the response `Survived`  
   - Any predictions on wether the passenger survived is going to deviate by 0.38 units (on average). The _lack of fit_ of the model is 0.38
   - Overall, the model has an R-squared from 0.3806. This tells us that 38.06% of the variability in whether the person survived can be explained by their class and sex

*** 
##### Fit a model containing the interactions between `Sex` and `age`. Interpret the coefficients.
```{r echo = FALSE}
summary(lm("Survived~Age*Sex",data = titanic_train))
```

***
##### Fit a model containing the interactions between `Sex`, `Pclass` and `age`. Interpret the coefficients.
```{r echo = FALSE}
summary(lm("Survived~Pclass+Sex+Age",data = titanic_train))
```
   
