---
title: "HW_ProbDistribution"
author: "Yilun"
date: "4/27/2021"
output:
   html_document:
    #variant: markdown_github
    toc: true
    number_sections: false
    self_contained: no
    toc_depth: 3
    toc_float: true
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Distributions in R

Every distribution that R handles has four functions. There is a root name, for e.g. the root name for the normal distribution is norm. This root is prefixed by one of following letters:

* p for probability, the cumulative distribution function 
* q for quantile, the inverse cumulative distribution function 
* d for density, the density function or probability function
* r for random, a random variable having the specified distribution

### Distribution functions for normal distribution

* `dnorm(x, mean = 0, sd = 1, log = FALSE)`
* `pnorm(q, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE)`
* `qnorm(p, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE)`
* `rnorm(n, mean = 0, sd = 1)`

## Excercise

### 1. Difference of Two Random Variable

Let X~N(mean = 3, sd =1 )

Let Y~N(mean = 2, sd = 2)

X and Y are statiscally independent

Task 1: What is P(X>Y)? Hint: Define Z = X-Y
```{r}
meanX = 3
meanY = 2
varX = 1
varY = 2
#Get distribution of Z=X-Y
meanZ= meanX-meanY
varZ = varX^2+varY^2

# For P(X>Y), Z > 0
# Calculate P(X>Y)
1-pnorm(0,mean = meanZ,sd = sqrt(varZ))
```

Task 2: Implement code that solves the task, i.e. create a function `my.simulation(n.reps, mu.x, mu.y, sigma.x, sigma.y)` where `n.reps` governs the number of repetitions / the precision of the simulation.
```{r}
my.simulation = function(n.reps, mu.x, mu.y, sigma.x, sigma.y){
  simDifference= rnorm(n.reps, mean=mu.x, sd=sigma.x)-rnorm(n.reps, mean=mu.y, sd=sigma.y)
  relevant = which(simDifference>0)
  probability = length(relevant)/n.reps
  return(probability)
  
}

my.simulation(100,3,2,1,2)
my.simulation(1000,3,2,1,2)
my.simulation(1000000,3,2,1,2)
```

### 2. Prob Calculator
Write a function that calculates P (x 1 ≤ X ≤ x 2 ) where X follows a normal distribution with parameters μ (mean) , σ (var).  The function input is a matrix with four columns. The first column refers to x1 , the second to x2 , the third to μ , the fourth to σ.  Each row can contain different values.  The output of the function is a vector having the same length as there are rows in the matrix.

```{r}
# Input Matrix:
my.matrix = matrix(nrow=2, ncol=4)
my.matrix[1,] = c(-1, 1, 0, 1)
my.matrix[2,] = c(-1, 2, 0, 1) 
colnames(my.matrix) <- c("x1", "x2", "mean", "sigma") 
my.matrix
```
```{r}
my.prob.calc = function(inputMatrix){
  x1.prob = pnorm(inputMatrix[,1], mean = inputMatrix[,3], sd=inputMatrix[,4])
  x2.prob = pnorm(inputMatrix[,2], mean = inputMatrix[,3], sd=inputMatrix[,4])
  result = x2.prob - x1.prob
  return(result)
}

#Checking
my.prob.calc(my.matrix)
```

