---
title: "Matrices"
author: "Yilun"
date: "4/20/2021"
output:
   html_document:
    #variant: markdown_github
    toc: true
    number_sections: false
    self_contained: no
    toc_depth: 2
    toc_float: true
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

`matrix()`constructs a matrix in R

### Syntax
`matrix(data = NA, nrow = 1, ncol = 1, byrow = FALSE,dimnames = NULL)` 

`data`:a Vector that gets arranged into a Matrix  
`nrow` and `ncol`: desired number of rows/columns optional
`byrow`: boolean,if false (default) the matrix is filled by columns, otherwise by rows  
`dimnames`: NULL (default) or a list of length 2 giving the row and column names respectively.An empty list is treated as NULL, and a list of length one as row names. The list can be named, and the list names will be used as names for the dimensions.  

EXAMPLE
```{r}
mdat <- matrix(c(1,2,3, 11,12,13), nrow = 2, ncol = 3, byrow = TRUE,
               dimnames = list(c("row1", "row2"),
                               c("C.1", "C.2", "C.3")))
mdat
```
***
### Methods
Example Dataset being 
```{r}
# Box office Star Wars (in millions!)
new_hope <- c(460.998, 314.4)
empire_strikes <- c(290.475, 247.900)
return_jedi <- c(309.306, 165.8)
phantom_menace = c(474.5, 552.5)
attack_clones = c(310.7, 338.7 )
revenge_sith = c(360.3, 468.5)
 
```
***
#### Combine multiple Vectors into Matrix:
```{r}
# Create box_office vector
box_office <- c(new_hope,empire_strikes,return_jedi)
box_office
# Construct star_wars_matrix
star_wars_matrix <-matrix(box_office,byrow=TRUE,3) 
star_wars_matrix

```
***
#### Naming a Matrix  
```{r}
# Vectors region and titles, used for naming
region <- c("US", "non-US")
titles <- c("A New Hope", "The Empire Strikes Back", "Return of the Jedi")
```
With `rownames()` and `colnames()`:
```{r}
## Name the columns with region
colnames(star_wars_matrix)<-region

## Name the rows with titles
rownames(star_wars_matrix)<-titles

# Print out star_wars_matrix
star_wars_matrix
```
With the attribute `dimnames`:
```{r}
#Option 2:
star_wars_matrix <- matrix(box_office,
                      nrow = 3, byrow = TRUE,
                      dimnames = list(titles, region))
# Print out star_wars_matrix
star_wars_matrix
```
***
#### Adding data: 
Add a Column `cbind()`:
```{r}
# adding the vector worldwide_vector as columns to Matrix
all_wars_matrix <- cbind(star_wars_matrix,rowSums(star_wars_matrix))
all_wars_matrix
```
 
Add a Row `rbind()`:
```{r}
# new vector of additonal Movies
newMovies = c(phantom_menace,attack_clones,revenge_sith)
# adjust title list
titles = c("The Phantom Menace","Attack of the Clones","Revenge of the Sith")
#create additionam Matrix
star_wars_matrix2 = matrix(
                          newMovies,
                          nrow = 3,
                          byrow = TRUE,
                          dimnames = list(titles,region)
                          )
# Add new Matrix to star_wars_matrix
all_wars_matrix <-rbind(star_wars_matrix,star_wars_matrix2) 
all_wars_matrix
```
***
#### Calculation in Matrix:  
Calculate Row sums `rowSums()`:
```{r}
# Calculate worldwide box office figures
worldwide_vector <- rowSums(star_wars_matrix)
worldwide_vector
```
Calculate Column sums `colSums()`:
```{r}
# Total revenue for US and non-US
total_revenue_vector <- colSums(all_wars_matrix)

# Print out total_revenue_vector
total_revenue_vector
```
***

#### Select Matrix Elements
Similar to vectors, you can use the square brackets `[ ]` to select one or multiple elements from a matrix. Whereas vectors have one dimension, matrices have two dimensions. You should therefore use a comma to separate the rows you want to select from the columns. For example:  

* `my_matrix[1,2]` selects the element at the first row and second column.
* `my_matrix[1:3,2:4]` results in a matrix with the data on the rows 1, 2, 3 and columns 2, 3, 4.  

If you want to select all elements of a row or a column, no number is needed before or after the comma, respectively:  

* `my_matrix[,1]` selects all elements of the first column.
* `my_matrix[1,]` selects all elements of the first row.
```{r}
# Select the non-US revenue for all movies
non_us_all <- all_wars_matrix[,"non-US"]
  non_us_all
# Average non-US revenue
mean(non_us_all)
  
# Select the non-US revenue for first two movies
non_us_some <- all_wars_matrix[1:2,2]
  
# Average non-US revenue for first two movies
mean(non_us_some)
```
***
#### Arithmetic operations with matrices
Similar to what you have learned with vectors, the standard operators like `+`, `-`, `/`, `*`, etc. work in an element-wise way on matrices in R.

For example, `2 * my_matrix` multiplies each element of `my_matrix` by two.
```{r}
# Estimate the visitors
visitors <- all_wars_matrix/5
  
# Print the estimate to the console
visitors
```
Just like `2 * my_matrix` multiplied every element of `my_matrix` by two, `my_matrix1 * my_matrix2` creates a matrix where each element is the product of the corresponding elements in `my_matrix` and `my_matrix2`.
```{r}
#init ticketprices
titles = c("A New Hope", "The Empire Strikes Back", "Return of the Jedi","The Phantom Menace","Attack of the Clones","Revenge of the Sith")
ticket_prices_matrix = matrix(c(5.0,5.0,6.0,6.0,7.0,7.0,4.0,4.0,4.5,4.5,4.9,4.9),nrow = 6,ncol = 2,byrow = TRUE,dimnames = list(titles,region))

# Estimated number of visitors
visitors <- all_wars_matrix/ticket_prices_matrix

# US visitors
us_visitors <- visitors[,1]

# Average number of US visitors
mean(us_visitors)
```

